---
title: "Reproducibility in R Training Day"
author: "Duncan Street"
date: "18 February 2020"

output: 
  html_document:
    toc: true
    toc_depth: 2
    toc_float: true

---
\

# Introduction
This is a introduction to reproducibility in R

\

## Starting with RStudio - Text formatting options {#start-header}
Information about RStudio

You can add **bold text** or __bold text with underscores__

You can also use *italics text* with _single underscores_

Adding superscript ^is_also_easy^

Adding subscript using ~tilde_sign~

If you add inline code use the backtick `to write code`

USe strikethrough text ~~double~~ tilde

If you're writing a lot of text
then you might want to break it up.

Another way is to use the \
backslash

You can also create a link like this: [Link to bioinformatics website](https://training.cam.ac.uk/bioinformatics/event-timetable)


But you might have some link to the footnote [^1].

[^1]: This is my first footnote

## Lists

1. Item 1
2. Item 2
3. Item 3
    a. Item 3a
        i. Item 3ai
        ii. Item 3aii
    b. Item 3b
    c. Item 3c
4. Item 4


* Item a
* Item b
* Item c
    * Item c1
    * Item c2
    * Item c3
        * Item c3i
        * Item c3ii


- Item 1
- Item 2
- Item 3


### Tasks

- [ ] an unchecked task list item
- [x] checked item


### Link images

![Remote University of Cambridge logo](https://cdn.worldvectorlogo.com/logos/university-of-cambridge.svg)


![Local University of Cambridge logo](images/university-of-cambridge.svg)



#### Tables

You can create tables using | -

| Column header | Another Column |
| ------------- | -------------- |
| First row     | With info      |
| More rows     | More info      |


> A greater than sign creates blocks


Single `backticks` are used inline.

```
print("hello world")
read.csv("data.csv")
```


```{r}
75*8
```


```{r}
calculation_output <- 100*2

calculation_output
```

```{r}
calculation_output*5
```


```{r}
download.file(url="https://raw.githubusercontent.com/cambiotraining/reproducibility-training/master/data/gapminder_data.csv", destfile="data/gapminder_data.csv")
```



Link back to header [link to header](#start-header)

